Type-theoretical Semantics of \Pio\ via the Delay Monad \thanks{Supported by organization x.}

### 2019-04-25 mpc19/paper.tex
Added rough abstract.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{Type-theoretical Semantics of \Pio\ via the Delay Monad \thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robin Kaarsgaard \inst{1}\orcidID{0000-0002-7672-799X} \and
Niccol\`o Veltri\inst{2}\orcidID{0000-0002-7230-3436}}
%
\authorrunning{Kaarsgaard and Veltri}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIKU, Department of Computer Science, University of
    Copenhagen\\ \email{robin@di.ku.dk} \and
Department of Computer Science, IT University of
    Copenhagen\\ \email{nive@itu.dk}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\todo{Write it!}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads,a4paper]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{Type-theoretical Semantics of \Pio\ via the Delay Monad \thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robin Kaarsgaard \inst{1}\orcidID{0000-0002-7672-799X} \and
Niccol\`o Veltri\inst{2}\orcidID{0000-0002-7230-3436}}
%
\authorrunning{Kaarsgaard and Veltri}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIKU, Department of Computer Science, University of
    Copenhagen\\ \email{robin@di.ku.dk} \and
Department of Computer Science, IT University of
    Copenhagen\\ \email{nive@itu.dk}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Reversible computation studies computations which exhibit both forward and
backward determinism. Among others, it has been studied for half a century for
its applications in low-power computing, and forms the basis for quantum
computing.

Though certified program equivalence is useful for a number of applications
(e.g., certified compilation and optimization), little work on this topic has
been carried out for reversible programming languages. As a notable exception,
Carette and Sabry have studied the equivalences of the finitary fragment of \Pio, a reversible combinator calculus, yielding a two-level calculus of type isomorphisms and equivalences between them.

In this paper, we extend the two-level calculus of finitary \Pio{} to one for
full \Pio{} (i.e., with both recursive types and iteration by means of a
\trace{} combinator) using the \Delay{} monad, which can be regarded as a
``computability-aware'' analogue of the usual $\mathsf{Maybe}$ monad for
partiality. This yields a calculus of iterative (and possibly nonterminating)
reversible programs acting on user-defined dynamic data structures together
with a calculus of certified program equivalences between these programs.

\todo{Niccol\`o, anything to add? Feel free to edit.}
